Characterizing Execution Times on Realistic Programs

### 2017-10-14 mlppi-ksii17/review/review_response.tex

\newenvironment{myindentparQ}[1]%
{\begin{list}{}
         {\setlength{\leftmargin}{#1}}
          \item[]
}
{\end{list}}
\newcommand{\quo}[1]{\begin{myindentparQ}{.25in} {{\color{gray}{#1}}}\end{myindentparQ}}

\begin{document}

\title{Responses to Editor-in-Chief \& Reviewer Comments}
\author{}
\maketitle

\section*{Overview}\label{sec:overview}
We appreciate these good reviews. We appreciate the feedback and suggestions.

@@

Manuscript ID TIIS-IS-2017-Jul-0844 entitled ``MLPPI Wizard: An Automated Multi-level Partitioning Tool on Analytical Workloads" which you submitted to the KSII Transactions on Internet and Information Systems, has been reviewed.  The comments of the reviewer(s) are included at the bottom of this letter.

I am happy to inform you that the reviewer(s) have recommended publication, but also suggest some revisions to your manuscript.  Therefore, I invite you to respond to the reviewer(s)' comments and revise your manuscript.   Please go through the reviewers' comments carefully and then prepare for the revised paper and authors' response. Your revised paper will not be guaranteed to be accepted for publication in the TIIS journal. The editor and reviewers will again review the revised paper and authors’ response.

}

In this response letter we address each of the reviewers' comments with care. 
We have incorporated into the revision our response to each of them.

@@

\rev{
3. In addition to the revised manuscript, the authors are required to write the authors’ response answering the reviewers’ comments. In order to expedite the processing of the revised manuscript, please be as specific as possible in your response to the reviewer(s)' comments.
}

This written response letter satisfies your requirement. It includes the respective response to each of the two reviewer's comments.

\rev{
4. The authors’ response should be included in "the first page of the revised manuscript."
}

Yes, we include in our submission this letter that appears on the front page of the revised article.

@@

\rev{
[IMPORTANT]:  Your original files are available to you when you upload your revised manuscript.  Please delete any redundant files before completing the submission.
}

We deleted any redundant files during the uploading process.

\rev{
Because we are trying to facilitate timely publication of manuscripts submitted to the KSII Transactions on Internet and Information Systems, your revised manuscript should be uploaded "by 15-Oct-2017."  If it is not possible for you to submit your revision in the deadline, we may have to consider your paper as a new submission.
}

Today ({\bf\underline{October 14th, 2017 in KST}}), prior to the specified deadline of October 15, 2017, 
we're submitting this revision for further review. So no violation on the deadline.

@@

\rev{
The table in Page3 does not have any caption to introduces besides, its location is badly organized.
}

Thanks for the comments. To address your concern, we put in tabular form the table with its caption on page~2 (now, {\color{blue}Tab.~2}). 
Note that we tabularized other examples for better exposition in the introduction.

\rev{
The main contribution of the paper is so limited and needs to be extended in Section 1. 
}

We took out some contributions mentioned in (the previous) Section 2 (now Section 3) and then incorporated them into the contribution paragraph (on page~5 
in the revision), which is now substantially extended.

@@

\rev{ 
In the experiment environmental setting, the deployment in realistic datasets are missing and must be indicated for the reproduction of the future readers.  
}

%Even though our query workloads (similar to {\em q1} in Tab.~3) are synthetic, the queries were generated from a realistic query template, 
%which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. Please refer to the third and subsequent paragraphs in Section~5.1 (on page 16).
%The synthetic queries used for our experiments were generated from a realistic query template, which is from customer cases like reports and form templates. The queries are of type joining a fact table and a dimension table in a popular benchmark, representing a real analytical workload. 
%In addition, the proposed wizard allows for general expressions for partitioning definition as addressed in the solution paragraph in the introduction. Hence, the results on our workloads do not lose their validity on a real environment. For more details, please refer to the Solution paragraph in the introduction and the third and subsequent paragraphs in Section~5.1.
%Please see the paragraph of `Workload Generation \& Deployment' in Section~5.1: more specifically, the third to fifth
%paragraphs in that section, where we address the use of synthetic queries in general from to represent a realistic scenario and have a mention of reproducibility of our work.
Please see Section~5.1 (more specifically, the third to fifth paragraphs in that section), where we address the use of synthetic queries in general from to represent a realistic scenario. We do have a mention of reproducibility of our work (as described in the second-to-last paragraph).

@@

%Your confusion comes from Figure 5 in the original submission. The proposed wizard obviously outperforms the compared approaches: no partitioning (NO PPI) and a human expert (EXP). For better clarification, we removed that figure and instead provided a comparison table. Again, our query workloads are from the real benchmark, SSB, and our algorithm is still applicable to any other type of analytical workload, since the search space is driven by the query predicates extracted from the workload.
After reading your comment we realized that {\color{blue}Fig.~5}, which is now removed, was confusing. We replaced it by a comparison table (now {\color{blue}\underline{Tab.~9}} on page 19) that shows that the proposed wizard outperforms the compared approaches.

\newpage

\rev{
Also, Authors should give a more clear definition of the ``application type" used in the paper. For example, what information of applications are used and how to obtain this information. 
}

The application type of the proposed wizard is a \underline{physical database design tool} (fundamentally different from several existing works {\color{red}[4--6]}. Also note that any complex workload, giving many different partitioning options, can benefit from the automated wizard to find almost an optimal solution. For more details, please refer to the first, third, and fifth bullets in the Contribution paragraphs in Section~1 on page~5.

@@

\rev{
Last but not least backs to the background which is limited and some hot-related works are missing that are listed in i)"Using imperialist competition algorithm for independent task scheduling in grid computing" and ii) "A hybrid metaheuristic algorithm for Job scheduling on computational grids" that addressed the analytical workload exploitation in the real case studies that must be added in the background to make your work holistic for the future readers.
}

OK, we now have some mentions of the above two works compared to our work. Accordingly, we have added these two articles in the References ({\color{red}[27, 28]}). Please also note that we have moved the Related Work section (now Section~2) (on page~5) right after Section 1, to respond to a concern from another reviewer.

@@

\rev{
1. Abstract could be better write, in this reviewer point of view, the current abstract is not comprehensive.
}

OK. We totally rewrote the abstract to reflect this comment.

\rev{
2. The manuscript could be better organize as well. For instance, the related works section could be placed after introduction section no before conclusion.
}

A great suggestion. We have moved the Related Work section (now Section~2) upfront (on page 5), right after Section 1. Please also note that Section~2 is expanded with some new references ({\color{red}[27, 28]}) to address the concerns from another reviewer.

@@

\rev{
3. Providing a comparison table could be useful for readers.
}

Yes, we now provide {\color{blue}Tab.~9} for better clarity on the comparison.

@@

\rev{
4. Conclusion is too long.
}

OK, we shortened the Conclusion section, which now sounds more concise.

\rev{
5. Introduction section need more references.
}

We've added some references in the Contribution paragraph in Section~1 on page 5.

### 2018-03-08 pt_characterization/real_data/paper.tex
Characterizing draft

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT200]{
		\includegraphics[scale=0.43]{sort200_dist.eps}
		\label{fig:sort200_dist}
	}
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\caption{PT Histograms of SORT100 ... SORT800~\label{fig:sort1}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT1600]{
		\includegraphics[scale=0.43]{sort1600_dist.eps}
		\label{fig:sort1600_dist}
	}
	\subfigure[PT frequency on SORT3200]{
		\includegraphics[scale=0.43]{sort3200_dist.eps}
		\label{fig:sort3200_dist}
	}
	\caption{PT Histograms of SORT1600 and SORT3200~\label{fig:sort2}}
\end{figure}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows from 1000x1000 to 8000x8000 by the steps of 2{\small $\times$}..

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC1000]{
		\includegraphics[scale=0.43]{matc1000_dist.eps}
		\label{fig:matc100_dist}
	}
	\subfigure[PT frequency on MATC2000]{
		\includegraphics[scale=0.43]{matc2000_dist.eps}
		\label{fig:matc200_dist}
	}
	\subfigure[PT frequency on MATC4000]{
		\includegraphics[scale=0.43]{matc4000_dist.eps}
		\label{fig:matc400_dist}
	}
	\subfigure[PT frequency on MATC8000]{
		\includegraphics[scale=0.43]{matc8000_dist.eps}
		\label{fig:matc800_dist}
	}
	\caption{PT Histograms of MATC1000 ... MATC8000~\label{fig:matc}}
\end{figure}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major 
as the input sizes grows from 1K$\times$1K to 8K$\times$8K by the steps of 2{\small $\times$}.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR1000]{
		\includegraphics[scale=0.43]{matr1000_dist.eps}
		\label{fig:matr100_dist}
	}
	\subfigure[PT frequency on MATR2000]{
		\includegraphics[scale=0.43]{matr2000_dist.eps}
		\label{fig:matr200_dist}
	}
	\subfigure[PT frequency on MATR4000]{
		\includegraphics[scale=0.43]{matr4000_dist.eps}
		\label{fig:matr400_dist}
	}
	\subfigure[PT frequency on MATR8000]{
		\includegraphics[scale=0.43]{matr8000_dist.eps}
		\label{fig:matr800_dist}
	}
	\caption{PT Histograms of MATR1000 ... MATR8000~\label{fig:matr}}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT25]{
		\includegraphics[scale=0.43]{sort25_dist.eps}
		\label{fig:sort25_dist}
	}
	\subfigure[PT frequency on SORT50]{
		\includegraphics[scale=0.43]{sort50_dist.eps}
		\label{fig:sort50_dist}
	}
	\subfigure[PT frequency on SORT100]{
		\includegraphics[scale=0.43]{sort100_dist.eps}
		\label{fig:sort100_dist}
	}
	\subfigure[PT frequency on SORT200]{
		\includegraphics[scale=0.43]{sort200_dist.eps}
		\label{fig:sort200_dist}
	}
	\caption{PT Histograms of SORT25 ... SORT200~\label{fig:sort1}}
\end{figure}

\clearpage
\pagebreak

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT400]{
		\includegraphics[scale=0.43]{sort400_dist.eps}
		\label{fig:sort400_dist}
	}
	\subfigure[PT frequency on SORT800]{
		\includegraphics[scale=0.43]{sort800_dist.eps}
		\label{fig:sort800_dist}
	}
	\subfigure[PT frequency on SORT1160]{
		\includegraphics[scale=0.43]{sort1160_dist.eps}
		\label{fig:sort1160_dist}
	}
	\caption{PT Histograms of SORT400 ... SORT1160~\label{fig:sort2}}
\end{figure}

\clearpage
\pagebreak

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT2320 (Will be updated with the rest.)]{
		\includegraphics[scale=0.43]{sort2320_dist.eps}
		\label{fig:sort2320_dist}
	}
	\subfigure[PT frequency on SORT3200]{
		\includegraphics[scale=0.43]{sort3200_dist.eps}
		\label{fig:sort3200_dist}
	}
	\\
	\subfigure[PT frequency on SORT4640]{
		%\includegraphics[scale=0.43]{sort4640_dist.eps}
		\framebox(200,200){Will be available soon.}
		\label{fig:sort4640_dist}
	}
	\subfigure[PT frequency on SORT6400]{
		\includegraphics[scale=0.43]{sort6400_dist.eps}
		\label{fig:sort6400_dist}
	}
	\caption{PT Histograms of SORT2320 ... SORT6400~\label{fig:sort3}}
\end{figure}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC250]{
		\includegraphics[scale=0.43]{matc250_dist.eps}
		\label{fig:matc250_dist}
	}
	\subfigure[PT frequency on MATC500]{
		\includegraphics[scale=0.43]{matc500_dist.eps}
		\label{fig:matc500_dist}
	}
	\subfigure[PT frequency on MATC1024]{
		\includegraphics[scale=0.43]{matc1024_dist2.eps}
		\label{fig:matc1024_dist}
	}
	\subfigure[PT frequency on MATC1440]{
		\includegraphics[scale=0.43]{matc1440_dist.eps}
		\label{fig:matc1440_dist}
	}
	\caption{PT Histograms of MATC250 ... MATC1440~\label{fig:matc}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC2048]{
		\includegraphics[scale=0.43]{matc2048_dist2.eps}
		\label{fig:matc2048_dist}
	}
	\subfigure[PT frequency on MATC2880]{
		\includegraphics[scale=0.43]{matc2880_dist.eps}
		\label{fig:matc2880_dist}
	}	
	\subfigure[PT frequency on MATC4096]{
		\includegraphics[scale=0.43]{matc4096_dist2.eps}
		\label{fig:matc4096_dist}
	}	
	\subfigure[PT frequency on MATC5760]{
		\includegraphics[scale=0.43]{matc5760_dist.eps}
		\label{fig:matc5760_dist}
	}	
	\caption{PT Histograms of MATC2048 ... MATC5760~\label{fig:matc2}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATC8192]{
		\includegraphics[scale=0.43]{matc8192_dist2.eps}
		\label{fig:matc8192_dist}
	}
	\subfigure[PT frequency on MATC11520]{
		\includegraphics[scale=0.43]{matc11520_dist.eps}
		\label{fig:matc11520_dist}
	}
	\subfigure[PT frequency on MATC16000]{
		\includegraphics[scale=0.43]{matc16000_dist.eps}
		\label{fig:matc16000_dist}
	}
	\subfigure[PT frequency on MATC23040]{
		\includegraphics[scale=0.43]{matc23040_dist.eps}
		\label{fig:matc23040_dist}
	}
	\caption{PT Histograms of MATC8192 ... MATC23040~\label{fig:matc3}}
\end{figure}

%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATC1000]{
%		\includegraphics[scale=0.43]{matc1000_dist.eps}
%		\label{fig:matc100_dist}
%	}
%	\subfigure[PT frequency on MATC2000]{
%		\includegraphics[scale=0.43]{matc2000_dist.eps}
%		\label{fig:matc200_dist}
%	}
%	\subfigure[PT frequency on MATC4000]{
%		\includegraphics[scale=0.43]{matc4000_dist.eps}
%		\label{fig:matc400_dist}
%	}
%	\subfigure[PT frequency on MATC8000]{
%		\includegraphics[scale=0.43]{matc8000_dist.eps}
%		\label{fig:matc800_dist}
%	}
%	\caption{PT Histograms of MATC1000 ... MATC8000~\label{fig:matc}}
%\end{figure}

\clearpage
\pagebreak

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR250]{
		\includegraphics[scale=0.43]{matr250_dist.eps}
		\label{fig:matr250_dist}
	}
	\subfigure[PT frequency on MATR500]{
		\includegraphics[scale=0.43]{matr500_dist.eps}
		\label{fig:matr500_dist}
	}
	\subfigure[PT frequency on MATR1024]{
		\includegraphics[scale=0.43]{matr1024_dist2.eps}
		\label{fig:matr1024_dist}
	}
	\subfigure[PT frequency on MATR1440]{
		\includegraphics[scale=0.43]{matr1440_dist.eps}
		\label{fig:matr1440_dist}
	}
	\caption{PT Histograms of MATR250 ... MATR1440~\label{fig:matr}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR2048]{
		\includegraphics[scale=0.43]{matr2048_dist2.eps}
		\label{fig:matr2048_dist}
	}
	\subfigure[PT frequency on MATR2880]{
		\includegraphics[scale=0.43]{matr2880_dist.eps}
		\label{fig:matr2880_dist}
	}	
	\subfigure[PT frequency on MATR4096]{
		\includegraphics[scale=0.43]{matr4096_dist2.eps}
		\label{fig:matr4096_dist}
	}	
	\subfigure[PT frequency on MATR5760]{
		\includegraphics[scale=0.43]{matr5760_dist.eps}
		\label{fig:matr5760_dist}
	}	
	\caption{PT Histograms of MATR2048 ... MATR5760~\label{fig:matr2}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on MATR8192]{
		\includegraphics[scale=0.43]{matr8192_dist2.eps}
		\label{fig:matr8192_dist}
	}
	\subfigure[PT frequency on MATR11520]{
		\includegraphics[scale=0.43]{matr11520_dist.eps}
		\label{fig:matr11520_dist}
	}	
	\subfigure[PT frequency on MATR16000]{
		\includegraphics[scale=0.43]{matr16000_dist.eps}
		\label{fig:matr16000_dist}
	}
	\subfigure[PT frequency on MATR23040]{
		\includegraphics[scale=0.43]{matr23040_dist.eps}
		\label{fig:matr23040_dist}
	}
	\caption{PT Histograms of MATR8192 ... MATR23040~\label{fig:matr3}}
\end{figure}

%\begin{figure}[h]
%	\centering
%	\subfigure[PT frequency on MATR1000]{
%		\includegraphics[scale=0.43]{matr1000_dist.eps}
%		\label{fig:matr100_dist}
%	}
%	\subfigure[PT frequency on MATR2000]{
%		\includegraphics[scale=0.43]{matr2000_dist.eps}
%		\label{fig:matr200_dist}
%	}
%	\subfigure[PT frequency on MATR4000]{
%		\includegraphics[scale=0.43]{matr4000_dist.eps}
%		\label{fig:matr400_dist}
%	}
%	\subfigure[PT frequency on MATR8000]{
%		\includegraphics[scale=0.43]{matr8000_dist.eps}
%		\label{fig:matr800_dist}
%	}
%	\caption{PT Histograms of MATR1000 ... MATR8000~\label{fig:matr}}
%\end{figure}

\clearpage
\pagebreak
